---
title: "Replication of Study 3 by Kwan, Dai & Wyer,JR (2017, Journal of Consumer Research)"
author: "Shirley Agustin, Arushi Srivastava (arsrivastava@ucsd.edu), Elaine Young "
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    toc: true
    toc_depth: 3
---

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

## Introduction

This replication project is based on the third study that was run in the "Contextual Influences on Message Persuasion: The Effect of Empty Space" by Kwan, Dai, and Wyer,JR (2017, Journal of Consumer Research). In this study it was found that participants did not evaluate the statements with empty space highly. However, participants were able to recall more statements in the empty space rather than the ones in the limited space. This project will further our understanding of empty space in the field of advertising while also getting a better understanding of visual cues and verbal messages.

[GitHub Repository](https://github.com/ucsd-psych201a/kwan2017)

[Original Paper](https://github.com/ucsd-psych201a/kwan2017/tree/main/original_paper)

[Experimental Paradigm](https://ucsd-psych201a.github.io/kwan2017/)

## Methods

### Power Analysis

To preface, the following estimate is based on default inputs in G Power. The original paper did not report enough parameters to determine an effect size accurately. Based on the f-test that we ran on G Power, we found that for an effect size of 0.25 we would need an estimate of 102 participants to achieve 0.8 power.

### Design Overview

The factor that was manipulated in this study was the empty spaces surrounding the statements presented to the participants. These two conditions are labeled as limited space condition and empty space condition.

The measure that was taken in this study was a survey given to participants to understand favorability of the statements in different conditions. This measure was not repeated and the study used within-participants.

The experiment could not use between-participants as particpants need to be exposed to both conditions for the experiment to run.

Steps were not taken to reduce demand characteristics. The potential confounds in the study would be the amount of words in the statements selected and the themes of the statements. They may be more likely to recall quotes with a smaller amount of words and some themes may resonate with participants more which may cause participants to recall certain quotes.

### Planned Sample

The original study had ninety four US residents that were recruited on Mechanical Turk for a monetary incentive. The amount of the monetary incentive was not disclosed by the authors. Although in an independent study mentioned in the general discussion of the paper it was disclosed that participants were payed \$.20. The only known demographics in this sample was the mention of 36 male participants in the study.

There were no preselection rules mentioned in the study.

### Materials

"We will create ten statements drawn from social media, covering topics such as romance, happiness, and personal values. These statements will vary in length from 3 to 11 words and will be presented uniformly in terms of font type, size, text positioning, line spacing, paragraphing, and background graphics".

"In the Limited Space Condition, quotes will be shown in a box sized between 420 × 315 pixels and 660 × 165 pixels, with no extra space around the border. In the Empty Space Condition, quotes will be displayed in a box ranging from 960 × 720 pixels to 960 × 240 pixels, surrounded by significant empty space".

The materials above will be precisely the same.

The quotes that will be presented to the participants are the following:

1.  Keep calm and carry on.
2.  Men never remember but women never forget.
3.  The best mirror is an old friend.
4.  Happiness shared is happiness doubled.
5.  Love is shown more in deeds than in words.
6.  Every day is a chance to grow.
7.  Take each day one step at a time.
8.  A heart in love has no limits.
9.  Life is too precious to waste on regrets.
10. Make time for what makes you smile.

### Procedure

"Participants first completed a survey called 'Quotes-of-the-Year,' during which they evaluated 10 statements sourced from social media platforms like Twitter and Facebook. These statements varied in length from 3 to 11 words and addressed various topics, including ro- mance (e.g., 'try to reason about love and you will lose your reason'), happiness (e.g., 'life is too short for tears'), and personal values (e.g., 'follow your heart'). All statements were pre- sented in the same font type, size, text positioning, line spacing, paragraphing, and background graphics".

"In the limited space condition, each quote was displayed in a box measuring between 420 × 315 pixels and 660 × 165 pixels, with no extra space around the border. In contrast, the empty space condition featured a box size ranging from 960 × 720 pixels to 960 × 240 pixels, surrounded by significant empty space".

"Participants reviewed all 10 quotes in both conditions. After reading each quote, they indicated how much they liked it and how important they thought it was, using a scale from 1 (not at all) to 7 (very much). Their responses were averaged to create a single measure of message persuasiveness ( = .88). Additionally, the time spent evaluating each quote was recorded, with the total time serving as an indicator of message deliberation".

"Finally, participants reported their age and gender before being given the first few words of each quote as a cue and asked to recall it as accurately as possible."

### Analysis Plan

We plan to run F-tests to compare favorability, and response time between the empty space condition and the limited space condition.

### Differences from Original Study

Our group is going to select new messages to present to the participants. In the original appendix of the study there is only three pairs of examples provided. The group will select messages from social media. The findings in the original study claim that empty spaces will cause the messages to be rated less favorably. Therefore, the content of the messages should not play a big factor in recall rate and favorability.

### Methods Addendum (Post Data Collection)

You can comment this section out prior to final report with data collection.

#### Actual Sample

Sample size, demographics, data exclusions based on rules spelled out in analysis plan

#### Differences from pre-data collection methods plan

Any differences from what was described as the original plan, or “none”.

## Results

### Data preparation

a)  Data import and initial inspection

```{r}
data <-  read.csv("/Users/shirley/Downloads/PSYCH201A/replication_pilot 2/Data_3.csv", header = TRUE)

str(data)
summary(data) #inspect
head(data) #preview

read.csv("/Users/shirley/Downloads/PSYCH201A/replication_pilot 2/Data_3.csv", row.names = NULL, check.names = FALSE)
```


#Assigning conditions

```{r}
empty_space <- data$Response.Time[data$Condition == "empty_space"]
limited_space <- data$Response.Time[data$Condition == "limited_space"]
```

b)  Data Cleaning

```{r}
my_data <- na.omit(data)  # Removes rows with any NA values
### Convert space_condition to factor if not already
my_data$Condition <- as.factor(my_data$Condition)
### Checking for duplicates using (duplicated) to ensure no rows are repeated
```

c)  Defining exclusion criteria \### Removing participants with incomplete responses

```{r}
#my_data <- filter(my_data, complete_cases == TRUE)
```

d)  Final Preparation \### Check the structure after data preparation

```{r}
str(data)
summary(my_data)
```

```{r include=F}
#### Load Relevant Libraries and Functions
library("dplyr")
library ("lavaan")
#### Import data
#my_data <- read.csv(file.choose())
#### Data exclusion / filtering
sample_n(my_data, 10)
favor.ftest <- var.test(empty_space, limited_space)
time.ftest <- var.test(data$Response.Time[data$Condition == "empty_space"],
                       data$Response.Time[data$Condition == "limited_space"])
favor.ftest
favor.ftest$estimate
favor.ftest$p.value
time.ftest
time.ftest$estimate
time.ftest$p.value
```

# Justification of F test

The original study compares the favorability of empty spaces and limited space conditions. The comparison of two samples suggests that an F test should be used to test for variance. ANOVA will also be used in this analysis to determine if there is a significant difference between the two groups in the study.

The original study used an F-test or ANOVA to analyze this comparison, then using the same approach is consistent with replication goals, further justifying its use.

# Confirmatory analysis

# F test

```{r}
f_test_result <- var.test(empty_space, limited_space)
print(f_test_result)
```

# Perform ANOVA

```{r}
anova_result <- aov(Response.Time ~ Condition, data = my_data)
summary(anova_result)
```

For Pilot B the average time participants took to complete the Pilot B was around 6 minutes.

### Exploratory analyses

Any follow-up analyses desired (not required).

## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt. None of these need to be long.
